### 2022-06-17 paper/main.tex
added some figures

\par Furthermore, Figure (REF) displays a map of all Metropolitan Areas by the percentage of crime posts submitted to their respective subreddits. The darker the shade of green, the more posts discuss crime. The average crime discussion percentage lays at 3.5\%.

@@

\par To identify any potential trends in the population data, we take the mean crime discussion value of each bucket category. Figure (REF) displays the average min-max normalization score for the percentage of crime discussion based on population size. Here, the very small population bucket contains 161 members with an average normalized score of 0.196, the small bucket contains 113 members with an average score of 0.173, the medium bucket contains 54 members with an average score of 0.166, and the large bucket contains 56 members with an average score of 0.260.

\par Figure (REF) provides average normalized scores for documented crime to compare trends to crime discussion. We can see that as population increases, documented crime rates gradually increase. This trend is semi-reflected in the crime discussion data. Crime discussion scores are roughly equivalent for the very small, small, and medium buckets. However, the large population bucket has a significantly higher crime discussion score than the other buckets. The large population bucket has a 6\% greater score than the medium population bucket when comparing documented crime data, but the large population bucket has a 56\% greater score than the medium population bucket when comparing crime discussion data.

@@

\par Similarly to population data, political affiliation is one possible variable that can sway crime discussion. To measure this, we look at the results of the 2020 presidential election. We consider the number of votes that the Democratic and Republic parties received as stand-ins for liberal and conservative political views, respectfully. Political affiliation of the 384 MSAs is broken down into the five categories discussed earlier: very conservative, conservative, moderate, liberal, and very liberal. Figure (REF) shows a map of the political affiliation of all Metropolitan Areas in the United States.

\par In identifying trends based on politics, we follow a familiar method and take the mean crime discussion value of each political class. Figure (REF) displays the average min-max normalization score for crime discussion and reported crime for each political class. Here, the very conservative bucket contains 112 members with a mean score of 0.170, the conservative bucket contains 103 members with a mean score of 0.179, the moderate bucket contains 57 members with a mean score of 0.207, the liberal bucket contains 73 members with a mean score of 0.201, and the very liberal bucket contains 39 members with a mean score of 0.274.

\par When looking at crime discussion rates, we can see that more liberal cities have the highest rates of crime discussion. The very liberal class has a 32\% higher crime discussion score than the next largest value. The two conservative political classes have the lowest crime discussion scores. However, these trends are not reflected in the documented crime rate scores. Figure (REF) shows that very liberal MSAs have a lower mean documented crime rate than more conservative areas. Very liberal areas are also the only class in which the crime discussion score is higher than the reported crime rate score.

@@

\begin{figure}[ht]
    \includegraphics[width=\textwidth]{Images/BingAerial.jpg}
    \caption{Aerial photograph of the Clock Tower, Peace Quad, and the Glenn G. Bartle Library Tower, June 16, 2009. This photograph was taken with a camera attached to a remote-controlled helicopter.}
    \label{fig:fig-2}
\end{figure}

>>>>

\par Furthermore, Figure \ref{fig:map-1} displays a map of all Metropolitan Areas by the percentage of crime posts submitted to their respective subreddits. The darker the shade of green, the more posts discuss crime. The average crime discussion percentage lays at 3.5\%.

\begin{figure}[ht]
    \includegraphics[width=\textwidth]{Images/PCrime.png}
    \caption{Map of crime discussion by MSA}
    \label{fig:map-1}
\end{figure}

@@

\par To identify any potential trends in the population data, we take the mean crime discussion value of each bucket category. Figure \ref{fig:graph-1} displays the average min-max normalization score for the percentage of crime discussion based on population size. Here, the very small population bucket contains 161 members with an average normalized score of 0.196, the small bucket contains 113 members with an average score of 0.173, the medium bucket contains 54 members with an average score of 0.166, and the large bucket contains 56 members with an average score of 0.260.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.75\textwidth]{Images/bar-population.png}
    \caption{Comparison of discussed crime and documented crime by population}
    \label{fig:graph-1}
\end{figure}

\par Figure \ref{fig:graph-1} provides average normalized scores for documented crime to compare trends to crime discussion. We can see that as population increases, documented crime rates gradually increase. This trend is semi-reflected in the crime discussion data. Crime discussion scores are roughly equivalent for the very small, small, and medium buckets. However, the large population bucket has a significantly higher crime discussion score than the other buckets. The large population bucket has a 6\% greater score than the medium population bucket when comparing documented crime data, but the large population bucket has a 56\% greater score than the medium population bucket when comparing crime discussion data.

@@

\par Similarly to population data, political affiliation is one possible variable that can sway crime discussion. To measure this, we look at the results of the 2020 presidential election. We consider the number of votes that the Democratic and Republic parties received as stand-ins for liberal and conservative political views, respectfully. Political affiliation of the 384 MSAs is broken down into the five categories discussed earlier: very conservative, conservative, moderate, liberal, and very liberal. Figure \ref{fig:map-2} shows a map of the political affiliation of all Metropolitan Areas in the United States.

\begin{figure}[ht]
    \includegraphics[width=\textwidth]{Images/pol.png}
    \caption{Map of 2020 Presidential Election Results by MSA}
    \label{fig:map-2}
\end{figure}

\par In identifying trends based on politics, we follow a familiar method and take the mean crime discussion value of each political class. Figure \ref{fig:graph-2} displays the average min-max normalization score for crime discussion and reported crime for each political class. Here, the very conservative bucket contains 112 members with a mean score of 0.170, the conservative bucket contains 103 members with a mean score of 0.179, the moderate bucket contains 57 members with a mean score of 0.207, the liberal bucket contains 73 members with a mean score of 0.201, and the very liberal bucket contains 39 members with a mean score of 0.274.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.75\textwidth]{Images/bar-politics.png}
    \caption{Comparison of discussed crime and documented crime by politics}
    \label{fig:graph-2}
\end{figure}

\par When looking at crime discussion rates, we can see that more liberal cities have the highest rates of crime discussion. The very liberal class has a 32\% higher crime discussion score than the next largest value. The two conservative political classes have the lowest crime discussion scores. However, these trends are not reflected in the documented crime rate scores. Figure \ref{fig:graph-2} shows that very liberal MSAs have a lower mean documented crime rate than more conservative areas. Very liberal areas are also the only class in which the crime discussion score is higher than the reported crime rate score.

\begin{figure}[!tbp]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{Images/scatter-politics-mid-large.png}
    \caption{Perceived crime by political leaning}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{Images/scatter-crime-mid-large.png}
    \caption{Documented crime by political leaning}
  \end{minipage}
\end{figure}

@@
